%****************************************************
%	CHAPTER 7 - Recommendations
%****************************************************
\chapter{Recommendations}
\label{chap:recommendations}
%====================================================
The short time length of this project, as well as the limited scope, which focused solely on the extraction of wave parameters from \acs{s1a} data, leaves several aspects of this project unexplored. This preliminary investigation is expected to provide valuable insights for future projects within the Antarctic research group at UCT, enabling a fully implemented pipeline for extracting sea ice parameters from \acs{sar} data to be developed. This short chapter is intended to introduce recommendations for the development of future pipelines.

\section{General Recommendations} \label{sec:rec.general}
\begin{itemize}
    \item Allocate sufficient time to gain access to \acs{csir} directional wave data.
    \item Assess the pipeline's robustness by using \acs{sar} data from various satellites operating at different bands. 
\end{itemize}

\section{Pre-processing} \label{sec:rec.preProcess}

\begin{itemize}
    \item Explore alternative and additional pre-processing techniques for \acs{s1a} data. These may include but are not limited to Ellipsoid Correction, Multi-looking, and Radiometric Calibration using gamma and beta options.
    \item Enhance the pre-processing component of the pipeline by using the \acs{snap} Python library to execute pre-processing commands for the downloading \acs{s1a} data.    
    \item Develop scripts for the seamless automated retrieval of \acs{s1a} data from the \textsc{Matlab} pipeline.
\end{itemize}

\section{\acs{sar} Imaging of Ocean Waves} \label{sec:rec.hh}
Since this project served as an initial exploration into the development of a wave parameter extraction pipeline, only the \acs{hh} technique was implemented. Future iterations of this pipeline should include the implementation of other wave parameter extraction algorithms. The following research papers are all centred around the \acs{hh} technique but optimise different aspects of the process. All of these algorithms are discussed in Chapter \ref{chap:litReview}.

\begin{itemize}
    \item “\acs{sar}-Ocean Wave Inversion using Image Cross Spectra” \cite{Engen1995}.
    \item “A semiparametric algorithm to retrieve ocean wave spectra from \acs{sar}” \cite{Mastenbroek2000}.
    \item “Toward an optimal inversion method for \acs{sar} wind retrieval” \cite{Portabella2002}.
\end{itemize}





%****************************************************
% END
%****************************************************
